---
title: "What Influences ToothGrowth"
author: "Thomas Jo"
date: '2021 6 12 '
output: html_document
---

**First**  We have to load the dataset **"ToothGrowth"**.


```{r echo=TRUE}
library(datasets)
library(ggplot2)

data("ToothGrowth")
```

Let's see the inside of ToothGrowth Dataset.

```{r echo=TRUE}
str(ToothGrowth)
```

We notice there are 60 observations and 3 variables in the dataset. Let's use other functions to search more information.


- **Summary function**


```{r echo=TRUE}
summary(ToothGrowth)
```
There are 2 levels of factor in supp, it's **OJ** AND **VC**, each has 30 observations. 


- **Unique function**


```{r echo=TRUE}
unique(ToothGrowth$dose)
```

We notice that they only took 0.5, l.0, 2.0 doses in this measurement. 

So far we found enough information to analyze the ToothGrowth Dataset. 


### **1. Differences between two Supplements**


```{r echo=TRUE}
 ggplot(ToothGrowth,aes(supp,len)) + geom_boxplot(aes(fill=supp)) + xlab("Supplement")+ ylab("Tooth length")
```


### **2. Differences from the amount of doses**
 
 
```{r echo=TRUE}
g <- ggplot(ToothGrowth,aes(x=factor(dose),y=len)) + geom_boxplot(aes(fill=factor(dose))) + 
  xlab("Doses")+ylab("Tooth length")

g + labs(title="Relationship between Tooth length and the amount of doses")

```

We can see that the increase of Dosage influence the Tooth Length.



### **3. Confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose**
 
 - **.5 Dose** 
 
```{r echo=TRUE}
t.test(len~supp,ToothGrowth[ToothGrowth$dose == .5,])
```


 - **1.0 Dose**

```{r echo=TRUE}
t.test(len~supp,ToothGrowth[ToothGrowth$dose == 1,])
```





 - **2.0 Dose**

```{r echo=TRUE}
t.test(len~supp,ToothGrowth[ToothGrowth$dose == 2,])
```



### **4. Conclusion**
 
 Only the usage of 2.0 dose fails to reject the null hypothesis. Other dosage of T-test P-value are less than 0.5, .5 dose P-value is **0.006359** and 1.0 dose P-value is **0.001038**. But the 2.0 dose's p-value is **0.9639**.
 
It means that using .5 dose and 1.0 dose of the supplement makes a significant difference between the group **OJ** AND **VC**. But when the dosage increases up to 2.0, there was no significant difference between group **OJ** AND **VC**. That is why they failed to reject the null hypothesis.
